XXX in a Tracing JIT Compiler for Efficient Dynamic Languages

### 2011-03-26 talk/icooolps2011/paper.tex
some notes about related work out of a discussion with samuele

@@

>>>>

partial evaluation \cite{futamura_partial_1999} \cite{jones_partial_1993}

earlier examples of promotion \cite{carl_friedrich_bolz_towards_????}, \cite{armin_rigo_jit_2007}

meta-tracers: SPUR \cite{bebenita_spur:_2010}
tamarin/lua stuff \cite{yermolovich_optimization_2009}
Dynamo \cite{sullivan_dynamic_2003}

\cite{chambers_efficient_1989} maps
\cite{hoelzle_optimizing_1994} Type feedback
\cite{hoelzle_optimizing_1991} PICs
find the web page of V8 about maps

is there anything about versions? smalltalks tend to clear their method caches
when new methods are added. self and java use dependency tracking and
deoptimization. this is better what we have above, because we need runtime
checks. mention out of line guard?

jruby used versions at some point, jvm-l mailing list discusses them

@@

invokedynamic tries to give control to the language implementor about PICs and
deoptimization
